Generalized Plackett-Luce Likelihoods

### 2022-09-28 inst/jss_hyper3.Rnw
house style for p-value and edition

Thus the additional support gained in moving from $a=\frac{1}{2}$ to
the evaluate of $a=\sqrt{2}-1$ is 0.029, rather small [as might be
expected given that we have only one rather uninformative observation,
and also given that the maximum likelihood estimate ($\simeq 0.41$) is
quite close to the null of $0.5$].  Nevertheless we can follow
\cite{edwards1972} and apply Wilks's theorem for a $p$-value:

@@

The $p$-value is about 0.81, exceeding 0.05; thus we have no strong
evidence to reject the null of $a=\frac{1}{2}$.  The observation is
informative, in the sense that we can find a credible interval for
$a$.  With an $n$-units of support criterion the analytical solution to
$\mathcal{S}(p)=-n$ is given by defining $X=\log(3-2\sqrt{2})-n$ and
solving $p(1-p)/(1+p)=X$, or
$p_\pm=\left(1-X\pm\sqrt{1+4X+X^2}\right)/2$, the two roots being the
lower and upper limits of the credible interval;
Figure~\ref{ABA_likelihood}.

@@

Above, we use generic function \code{equalp.test()} to test the null
that the permeability of the two groups both have Bradley-Terry
strength of $0.5$.  We see a p-value of about 0.09; compare 0.25 from
\code{wilcox.test()}.  However, observe that the \code{hyper3}
likelihood approach gives more information than Wilcoxon's analysis:
Firstly, we see that the maximum likelihood estimate for the
Bradley-Terry strength of \code{x} is about 0.24, considerably less
than the null of 0.5; further, we may plot a support curve for this
dataset, given in Figure~\ref{wilcox_likelihood}.

>>>>

Thus the additional support gained in moving from $a=\frac{1}{2}$ to
the evaluate of $a=\sqrt{2}-1$ is 0.029, rather small [as might be
expected given that we have only one rather uninformative observation,
and also given that the maximum likelihood estimate ($\simeq 0.41$) is
quite close to the null of $0.5$].  Nevertheless we can follow
\cite{edwards1972} and apply Wilks's theorem for a $p$~value:

@@

The $p$~value is about 0.81, exceeding 0.05; thus we have no strong
evidence to reject the null of $a=\frac{1}{2}$.  The observation is
informative, in the sense that we can find a credible interval for
$a$.  With an $n$-units of support criterion the analytical solution to
$\mathcal{S}(p)=-n$ is given by defining $X=\log(3-2\sqrt{2})-n$ and
solving $p(1-p)/(1+p)=X$, or
$p_\pm=\left(1-X\pm\sqrt{1+4X+X^2}\right)/2$, the two roots being the
lower and upper limits of the credible interval;
Figure~\ref{ABA_likelihood}.

@@

Above, we use generic function \code{equalp.test()} to test the null
that the permeability of the two groups both have Bradley-Terry
strength of $0.5$.  We see a $p$~value of about 0.09; compare 0.25 from
\code{wilcox.test()}.  However, observe that the \code{hyper3}
likelihood approach gives more information than Wilcoxon's analysis:
Firstly, we see that the maximum likelihood estimate for the
Bradley-Terry strength of \code{x} is about 0.24, considerably less
than the null of 0.5; further, we may plot a support curve for this
dataset, given in Figure~\ref{wilcox_likelihood}.
